--- 
title: "Probability Models"
author: "Katherine Wilson"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---

# Beta and Gamma

## gamma function

Gamma of something plus 1 over the gamma of something equals that same something

$$\begin{equation}
\Gamma(a) = \int_{0}^{\infty}t^{\alpha-1}e^{-t}dt, \alpha >0
\end{equation}$$

$$\begin{equation}
\frac{\Gamma(a+1)}{\Gamma(a)} = \alpha
\end{equation}$$

## beta function

Beta function defined by
$$\begin{equation}
B(a,b) = \int_{0}^{\infty}t^{\alpha-1}(1-t)^{b-1}dt, b >0
\end{equation}$$


Beta can be expressed as a fraction of gamma functions.

$$\begin{equation}
B(a,b) = \frac{\Gamma(a)\Gamma(b)}{\Gamma(a+b)}
\end{equation}$$

PDF of beta, expressed by alpha and beta
$$\begin{equation}
f(\theta|alpha,\beta) = \frac{\theta^{\alpha-1}(1-\theta)^{\beta-1}}{\beta(\alpha,\beta)}
\end{equation}$$
Mean of the beta is
$$\begin{equation}
E(\theta) = \frac{\alpha}{\alpha+\beta}
\end{equation}$$

where $\alpha$ is the action parameter (pushes the beta distribution to the right of the graph). Means people have more propensity to churn, more values closer to 1 than 0 in our population, and $\beta$ is the inaction parameter (pushes the peak of the beta distribution to thel eft of the graph), meeans more values closer to 0 thatn 1, means a low propensity to churn. Compare $alpha$ and $\beta$ to 1, where either is high if it is greater than 1. If both $\alpha$ and $\beta$ = 1, results in uniform. 

## shapes of beta distribution


```{r}
#define range
p = seq(0, 1, length=100)

#create plot of Beta distribution with shape parameters 2 and 10
plot(p, dbeta(p, 5, 5), type='l', ylab = 'density',
     col = 'purple', main = "Beta Distribution")
lines(p, dbeta(p,1,1), col = 'red')
lines(p, dbeta(p,0.5,0.5), col = 'blue')
legend(.7, 4, c('Beta(5,5)','Beta(1,1)','Beta(0.5,0.5)'),
       lty=c(1,1,1),col=c('purple', 'red', 'blue'))

```


```{r}
#define range
p = seq(0, 1, length=100)

#create plot of Beta distribution with shape parameters 2 and 10
plot(p, dbeta(p, 1.5,0.5), type='l', ylab = 'density',
     col = 'purple', main = "Beta Distribution")
lines(p, dbeta(p,0.5,1.5), col = 'red')
lines(p, dbeta(p,2,4), col = 'blue')
legend(.7, 4, c('Beta(1.5,0.5)','Beta(0.5,1.5)','Beta(2,4)'),
       lty=c(1,1,1),col=c('purple', 'red', 'blue'))

```



